Combining information from photometric and spectroscopic data: Don't waste your time in spectral calibration!

### 2014-04-25 tex/ms.tex
asdfasd
asdfs
abstractStart

\begin{abstract}
Hello World!
\end{abstract}

@@

>>>>

\begin{abstract}
In a typical spectral-fitting project,
  there tend to be a small number of bands of well-calibrated photometry
  and thousands of poorly calibrated spectroscopic pixels.
Good spectroscopic calibration is both expensive and difficult,
  but naive weighted least-square fitting will weight
  the thousands of spectroscopic pixels far higher overall
  than the few photometric bands.
\end{abstract}

@@

\acknowledgements
Thanks in advance to X. for bringing us beer.
